Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-30 paper/ms.tex
model description

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $1.5\times
10^{9}$\hMsun\ resolved with at least  $10$ particles.

@@

We build a model to assign LAEs to a DM halo. 
We are not concerned on the exact LAE luminosity, we only care about a yes/no answer to the following question. Does this halo host a LAE?

We first assume that a dark matter halo can host one detectable LAE at most.  
This assumption is consistent with theoretical analysis of the correlation function \citep{Jose2013b} and observations that confirm a lack of class pairs in LAEs \cite{Bond2009}.

Then we say that a halo will host a LAE with probability $f_{\rm occ}$ if and only if the halo mass is in the range $M_{\rm min}< M_{\mathrm h} < M_{\rm max}$.
The probability $f_{\rm occ}$ can be thought as the occupation fraction of halos which can be automatically set as the ration of the observed number of LAEs to the number of halos within the considered mass range, that is $f_{\rm occ}\equiv N_{\rm LAE}/N_{\mathrm halos}$.

Fig. \ref{fig:cosmicv0}  shows the cumulative halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$. From this figure we can see that the number of dark matter halos along the mock fields for different models $\mathcal{M}$ varies within a factor of $\sim 2$ ($\sim 0.3$dex) tracing the cosmic variance. As a consequence, the occupation fraction varies along  the mock fields  by the same factor factor. The interpretation of the occupation fraction $f_{\rm occ}$ involves two phenomena: the actual presence of a star forming galaxy in a halo and its detectability as a LAE.

>>>>

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $1.5\times
10^{9}$\hMsun\ resolved with at least  $10$ particles. 
We do not take into account sub-halos.

@@

We build the simplest possible model to assign a LAE to each DM halo
without trying to compute a LAE luminosity.

We first assume that a dark matter halo can host one detectable LAE at
most.   
This assumption is consistent with theoretical analysis of the
correlation function \citep{Jose2013b} and observations that confirm a
lack of class pairs in LAEs \cite{Bond2009}.  
Then we say that a halo will host a LAE with probability $\focc$
if and only if the halo mass is in the range $\mmin < M_{\mathrm
  h} < \mmax$. 
In what follows we refer to a given set of values $\focc$, $\mmin$,
$\mmax$ as a model, $\mathcal{M}$. We also use a variable \dm to represent
the mass range width, $\dm\equiv\ \log \mmax - \log \mmax$.

The parameter $\focc$ can be thought as the LAE occupation fraction of
dark matter halos.
An astrophysical interpretation of $f_{\rm occ}$ convolves at least
three phenomena: the actual presence of a star forming galaxy in a
halo, the escape fraction of \ly\ radiation and its detectability as
a LAE.   
We do not try to disentangle these complex phenomena.
We instead opt for an arithmentic interpretation by setting $\focc$ as
the ratio between the observed number of LAEs and the number of halos
within the considered mass range, that is $\focc \equiv N_{\rm
  LAEs}/N_{\mathrm{halos}}$.

Fig. \ref{fig:cosmicv0}  shows the cumulative halo number density
for all 27 subvolumes in the simulation, with a normalization by the
average number density among fields. 
Each line represents a different model $\mathcal{M}$ with fixed
$\focc=1$ and $\dm=1.0$; and varying $\mmin$, 
This Figure shows that the halo number density varies across
sub-volumes, as an expression of cosmic variance. 
As a consequence, the $\focc$ also varies across the mock fields  
by the same factor factor.
